A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-13 graph_syntax.tex
update sellar problem

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \end{equation}
\end{description} 
These violations will be managed in order to seek a working problem formulation.

\section{Graph Representation of MDAO Constructs}
%As discussed in Sec.((intro)), the digraph must be able to describe the individual aspects of an MDAO problem.
\subsection{Analysis Blocks and Connections}
Analysis tools take in a number input variables and then perform some work to calculate 
the values for their respective outputs. In an MDAO graph, this process is 
represented by a group of nodes and edges called an \emph{analysis block}, 
shown in Fig. \ref{f:analysis block}. Within an analysis block each variable 
node represents a single input or output and is connected 
to a single model node via a fixed edge. Note that in Fig. \ref{f:analysis block}, 
the analysis block contains two model nodes, with a single edge connecting them. 
This edge represents the necessary calculations to map given inputs 
to proper output values. If constructing a weighted graph, the weight calculation edge 
provides the opportunity to computational cost. However, it is also allowed to skip 
this edge and have both incomming and outgoing edges to variables through a single model 
node for a given analysis block. Although analysis blocks are comprised of multiple nodes and edges, since all 
the edges within them are fixed, they become fixed sub-graphs within a graph.

\begin{figure}[htb!]
    \begin{center}
    \includegraphics[width=4in]{images/analysis_block}
    \end{center}
    \vspace{-10pt}
\caption{Example analysis block. The each node type and edge type is labeled in italics and annotated parenthetically.}
\label{f:analysis block}
\end{figure}

@@

MDAO problems require that information be passed between sets of analyses. When 
information from the output of one analysis block is passed, or connected, to the 
input of another analysis block, a new connection edge is added connecting the two 
variable nodes involved in the exchange. These connection edges are free, unlike the edges 
within an analysis block, they could be added or removed depending on the needs
of a given design problem. In other words, free connection edges are created by 
engineers linking the output of one tool to the input of another one. Note that 
it is allowed for a single output to have outgoing connection edges to multiple 
downstream inputs.

\subsection{Design Variables}
Design variables require external decisions 
to be made about a given system to identify them. Consider 
a notional problem given by the graph in Fig. \ref{f:designvars} There are three input variables 
which, could potentially become design variables: $w$, $x$, and $y$. Because the variable $x$ is connected from $A$ to $B$,
 $x$ can't actually be a design variable. On the other hand, the inputs $w$ and $y$
have no incomming edges and could each be selected as design variables. 
\begin{figure}[htb!]
  \begin{center}
    \includegraphics[width=.6\textwidth]{images/design_vars_graph}
  \end{center}
  \caption{Notional graph with two potential design variables \label{f:designvars}}
\end{figure}

Given a MCG with the ${deg}_l^-(v)=1$ for all nodes, there will be a set of holes. 
Each hole represents a node that could potentially become a design variable. 
It is up to the designer to examine that variable and decide if it is appropriate to 
use it as a design variable. If a variable should be a design variable, then 
set it's ${deg}_l^-(v)=0$. However, some variable holes might not make good design 
variables. For instance, if your aircraft mission analysis code requires a drag input 
which ends up being a hole then it's likely that some new analysis tool is needed
to predict drag before the design process can continue. In that case, you leave
${deg}_l^-(v)=1$ and find some tool to fill the hole in graph.

So by definition, a design variable is any variable node with ${deg}_l^-(v)=0$, 
When working with a MCG or FPG, only connection edges are allowed, so a design 
variable in either graph will be a variable with no edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
implicit edges from one or more driver nodes.

\subsection{Objectives, and Constraints}
Objectives and constraints are also constructs that need to be identified by engineers 
as part of the design process. In the case of objective functions single output values 
could be selected, but commonly multiple values are assembeled together via simple 
algebraic expression to form a objective function. For example, the problem from 
Fig. \ref{f:designvars} might have an objective function of $z^2$ or $2y + z$. Constraints are 
always given in the form of either an inequality of an equality, e.g. 
$\frac{2y}{10}-1<0$ or $3x+2y - 5=0$. In both cases, an engineer compiles an
algebraic expression that can be evaluated to produce an output.

These operations, though very simple, are effectively the same kind of task 
performed by an analysis block. A constraint or objective function can therfore 
be represented as another analysis block on the graph, with it's own input and 
output variable nodes. Although fundamentally no different than an analysis block, 
for clarity and convience it is useful to distinguish between regular analysis 
blocks and those that arise from the addition of objectives or constraints to 
the graph. So we define an expression block, as the collection of variable and model 
nodes related to a given objective or constraint function. Fig. \ref{f:obj-cons}
shows a notional problem graph augmented with expression blocks and appropriate 
connection edges.

\begin{figure}[htb!]
  \begin{center}
    \includegraphics[width=.6\textwidth]{images/obj_const_graph}
  \end{center}
  \caption{Notional graph with and objective and constraint nodes \label{f:obj-cons}}
\end{figure}

\subsection{Local vs Global Nodes}

  A simple definition of a global node is any node that involves information 
  from more than one analysis block. Likewise, a local node is any node 
  that involves information from only a single analysis block. As stated before, variable 
  nodes with fixed edges directed to model nodes (as part of an analysis block) are inherently local 
  and similarly model nodes are also local. Expression and driver nodes
  are not inherently local or global though. For these, their locality is determined 
  by the incomming and outgoing edges they possess. Consider the graph in Fig. \ref{f:local_global}, 
  where the expression node $g_1$ represents some kind of constraint for the optimziation problem. 
  Since $g_1$ only has edges comming from analysis block $B$, it would be considered a local constraint 
  on block $B$. $g_2$ has incomming edges from both $A$ and $B$ analysis blocks, so it would be a global constraint.

@@

  Although we've already established that variable nodes in an analysis block are local to that 
  block, global variables are a part of many MDAO problems and must be representable. A global variable 
  would be any variable node with multiple outgoing connection edges. 
  For example, in Fig. \ref{f:local_global} the global node $w^*$ has outgoing edges to 
  the $w$ variable nodes feeding both $A$ and $B$ analysis blocks.

  While this simple definition is valid, it glosses over a more subtle aspect of 
  some MDAO problems. Fig. \ref{f:local_global}, has three analysis 
  blocks A, B, and C. Above we identified node $g_2$ as global,  but
  it has no incomming edges from block $C$. So you could say that $g_2$ is 
  local to the the set of blocks $A,B$. In this sense, locality 
  becomes a relative term. A given node can be local to a specific sub-graph of a large
  problem. This subtle structure can become significant when determining how to 
  effectively partition an MDAO problem into sub-problems 
  \cite{krishnamachari1997optimal,allison2009optimal,michelena1997hypergraph}.

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. Consider the notional problem from section \ref{sec:spg_vs_fpg} where two 
  analyses, $A$ and $B$ are coupled through their respective variables. The graph of this 
  is shown in Fig. \ref{f:coupling}. In the graph $A.z$ has an outgoing connection 
  edge to $B.z$, indicating that there is a connection between the two. 
  Similarly a connection exists between $B.y$ and $A.y$. These two connections form 
  a cycle which represent the coupling between them. This cycle means that blocks $A$ and $B$ need
  to be iterated on untill they converge.

>>>>

  \item[collision: ] The number of incomming edges is greater than $ \txt{deg}_u^-(v)$. 
    \begin{equation} \txt{deg}^-(v) > \txt{deg}_u^-(v) \label{e:collision} \end{equation}
\end{description} 
These violations will be managed in order to seek a working problem formulation.

\section{Graph Representation of MDAO Constructs}
In this section we will make use of the Sellar problem, described in 
Eqn. \ref{eqn:simple_fpf}. The graph representation of the Sellar problem, 
using the new stynax, is presented in Fig. \ref{f:sellar_graph_full}. Throughout
the rest of this section, different sub-graphs or slight modifications of 
the full graph will be used to demonstrate the important MDAO constructs within
this graph syntax.

\begin{figure}[htb!]
    \begin{center}
    \includegraphics[width=4in]{images/sellar_graph_full}
    \end{center}
    \vspace{-10pt}
\caption{Graph of the Sellar problem formulation}
\label{f:sellar_graph_full}
\end{figure}

%As discussed in Sec.((intro)), the digraph must be able to describe the individual aspects of an MDAO problem.
\subsection{Analysis Blocks and Connections}
Analysis tools take in a number input variables and then perform some work to calculate 
the values for their respective outputs. In an MDAO graph, this process is 
represented by a group of nodes and edges called an \emph{analysis block}. 
The Sellar problem has two analyses, $D_1$ and $D_2$, so the graph will have 
two analysis blocks in it. Fig. \ref{f:analysis block} shows the analysis block for $D_2$
with some important annotations. Within an analysis block each variable 
node represents a single input or output and is connected 
to a single model node via a fixed edge.  Note that in Fig. \ref{f:analysis block}, 
the analysis block contains two model nodes, with a single edge connecting them. 
This edge represents the necessary calculations to map given inputs 
to proper output values. If constructing a weighted graph, the weight calculation edge 
provides the opportunity to represent computational cost. However, it is also fine to skip 
this edge and have both incomming and outgoing edges to variables through a single model 
node for a given analysis block. Although analysis blocks are comprised of multiple nodes and edges, since all 
the edges within them are fixed, they become fixed sub-graphs within a graph.

\begin{figure}[htb!]
    \begin{center}
    \includegraphics[width=4in]{images/analysis_block}
    \end{center}
    \vspace{-10pt}
\caption{Sellar problem $D_2$ analysis block The each node type and edge type is labeled in italics and annotated parenthetically.}
\label{f:analysis block}
\end{figure}

@@

MDAO problems require that information be passed between sets of analyses. When 
information from the output of one analysis block is passed, or connected, to the 
input of another analysis block, a new connection edge is added connecting the two 
variable nodes involved in the exchange. These connection edges are free, unlike the edges 
within an analysis block, they could be added or removed depending on the needs
of a given design problem. In other words, free connection edges are created by 
linking the output of one tool to the input of another one. Note that 
it is allowed for a single output to have outgoing connection edges to multiple 
downstream inputs.

\subsection{Design Variables}
For the Sellar problem, there are three design variables, $x_1^*$, $z_1^*$, and $z_2^*$. In Fig. 
\ref{f:sellar_graph_full}, these are the only three holes (nodes without out 
incomming edges) in the graph. Based on this example it's tempting to simply 
call all holes in the graph design variables. However, in the general case this is 
not completely correct. For any given problem, the set of holes only identifies 
all the potential design variables. However, some variable holes might not make good design 
variables. For instance, if your aircraft mission analysis code requires a drag input 
which ends up being a hole then it's likely that some new analysis tool is needed
to predict drag before the design process can continue.

\begin{figure}[htb!]
  \begin{center}
  [NOTE: Re-work this one to match $D_2$ from Sellar]
    \includegraphics[width=.6\textwidth]{images/design_vars_graph}
  \end{center}
  \caption{Notional graph with two potential design variables \label{f:designvars}}
\end{figure}

More formally stated, given a MCG with the ${deg}_l^-(v)=1$ for all nodes, 
there will be a set of holes. Each hole represents a node that could potentially 
become a design variable. It is up to the designer to examine that variable and 
decide if it is appropriate to use it as a design variable. If a variable should 
be a design variable, then set it's ${deg}_l^-(v)=0$. Otherwise you leave 
${deg}_l^-(v)=1$ and find some tool to fill the hole in graph.

So a design variable is defined as any variable node with ${deg}_l^-(v)=0$. 
This, by definition, means that design variables are not holes in the graph, since 
they have not violated their lower in-degree limit. Regardless, 
when working with a MCG or FPG, only connection edges are allowed, so a design 
variable in either graph will be a variable with no incomming edges edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
implicit edges from one or more driver nodes.

\subsection{Objectives, and Constraints}
Like design variables, objectives and constraints are also constructs that need 
to be identified when setting up a given design problem. In the case of 
objective functions single output values could be selected, but commonly multiple 
values are assembeled together via simple algebraic expressions to form a composite 
objective function. (e.g. The objective function from Eqn. \ref{eqn:simple_fpf} is
$x_1^2+z_2+y_1+e^{-y_2}$). Constraints are always given in the 
form of either an inequality or an equality. (e.g. a constraint from Eqn. 
\ref{eqn:simple_fpf} is $\frac{y_1}{3.16}-1\geq0$.) By convention, 
constraints are usually given such that some expression will be less than or equal 
to zero, so any positive value would violate the constraint. For both objective 
and constraints, these simple expressions take some inputs and map them to an
output value of significance to the overall design problem.

These operations, though very simple, are effectively the same task 
performed by an analysis block. A constraint or objective function can therfore 
be represented as another analysis block in the graph, with it's own input and 
output variable nodes. Although fundamentally no different than an analysis block, 
for clarity and convience it is useful to distinguish between regular analysis 
blocks and those that arise from the addition of objectives or constraints to 
the graph. So we define an expression block, as the collection of variable and model 
nodes related to a given objective or constraint function. Fig. \ref{f:obj-cons}
shows the objective and constraint blocks from the Sellar problem in isolation 
from the rest of the problem. Note how each block has it's own input variables, 
which in the full graph would be linked via connection edges. Treating objectives 
and constraints in this way introduces extra variables to the problem formulation,
but provides an important benefit for describing local and global properties of 
MDAO problems.

\begin{figure}[htb!]
  \begin{center}
    [NOTE: Show just the G1, G2, and F blocks from Sellar Graph]
    \includegraphics[width=.6\textwidth]{images/obj_const_graph}
  \end{center}
  \caption{Notional graph with and objective and constraint nodes \label{f:obj-cons}}
\end{figure}

\subsection{Local vs Global Properties}

  A simple definition of a global node is any node that involves information 
  from more than one analysis block. Likewise, a local node is any node 
  that involves information from only a single analysis block. As stated before, variable 
  nodes with fixed edges directed to model nodes (as part of an analysis block) are inherently local 
  and similarly model nodes are also local. Global variables are a part of many 
  MDAO problems and must be representable in the graph. Follwoing our simple definition
  any variable node that had multiple incomming or outgoing edges, would be global. 
  In Fig. \ref{f:sellar_graph_full} the variable nodes for $x_1^*$, $z_1^*$, and $z_2^*$ 
  have multiple outgoing edges and would be considered global.

  Note that the variable $x_1$ from the Sellar problem is usually refered to as 
  a local variable, which is contradicted by the given graph. This discrepancy 
  arises from the explicit treatment of objectives and constraints as separate 
  expression blocks. Normally in the Sellar problem $x_1$ is considered a local 
  variable because it only directly affects analysis block $D_1$. By forcing
  the expansion of $F$ into an expression block with its own inputs, then $F$ 
  gets it's own copy of the $x_1$ variable. This necessitates the creation 
  of the global $x_1^*$ node in the graph with two outgoing edges to link the 
  two $x_1$ inputs nodes in the different blocks. Interestingly, using this 
  definition, where $x_1^*$ is a global variable fits nicely within 
  the structure of Braun's Colaborative Optimization (CO) archtiecture \cite{braun_thesis}. 
  The rules of setting up a problem with CO require that each discipline be 
  given an independent local copy of all global variables, while any local 
  variables are retained uniquely within their respective disciplines. But 
  when a local design variable shows up explicitely in the objective function 
  or global constraint then a global variable is created, and the discipline again 
  gets an independent local copy of it. Given our definition of global vs local
  variable nodes, no such exception for local variables is necessary. When you 
  include a given variable in an expression node, it becomes global by definition 
  and should be treated as such in CO.

  Analysis and expression blocks can also have a locality defined for the set of 
  nodes and edges within the block. Their locality is determined by the 
  incomming and outgoing edges from the block as a whole. Fig. \ref{f:sellar_graph_full} has expression blocks for each constraint, $G_1$ and $G_2$. Both constraints are 
  local to their respective analysis blocks. But the expression block for $F$ 
  has incomming edges from $D_1$ and $D_2$, so it would considered global.

@@

  Simply stating that any node or block with incomming or outgoing edges
  from more than one other node or block is global works glosses over a more 
  subtle aspect of some MDAO problems. The locality of any node in a graph is 
  a relative property. For instance, a single node might have outgoing edges 
  to two separate analysis blocks, $A$ and $B$, but none to a third, $C$. Then 
  you could say that this node was global with respect to $A$ and $B$, but local 
  to the group $A,B$ with respect to $C$. This situation produces a natural 
  hierarchy in a graph, where you can form increasingly smaller groups as you 
  segment problem into finer localities. When solving a problem using 
  a heirarchical decomposition approach, there are various techniques for 
  partitioning that are effective in different scenarios 
  \cite{krishnamachari1997optimal,Perez2004,sobieszczanski1997,allison2009optimal,michelena1997hypergraph}.

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. Consider the notional problem from section \ref{sec:spg_vs_fpg} where two 
  analyses, $A$ and $B$ are coupled through their respective variables. The graph of this 
  is shown in Fig. \ref{f:coupling}. In the graph $A.z$ has an outgoing connection 
  edge to $B.z$, which refers to the coupling constraint $g1$ from Eqn. \ref{eqn:simple_fpf}. Similarly a connection exists between $B.y$ and $A.y$ refering to the coupling constraint
  These two connections form a cycle which represent the coupling between them. This cycle means that blocks 
  $A$ and $B$ need to be iterated on until the two equality constraints from Eqn. \ref{eqn:simple_fpf}.

### 2013-04-13 intro.tex
update sellar problem

    The Fundamental Problem Formulation (FPF) for any given problem will be constant regardless 
    of which MDAO framework, optimization algorithm, iterative solver, or solution strategy
    is used to solve the problem. For example, consider the following notional problem:

    \begin{align}
        given & \ \ A: {x,y} \rightarrow {m,z} \notag
        \\      & \ \ B: {x,z} \rightarrow {y^t} \notag
        \\min. &\ \ f(m) \notag
        \\w.r.t. & \ \ x,y,z \notag
        \\s.t. & \ \ g(y^t,y) = 0
        \label{eqn:simple}
    \end{align}

    $A$ and $B$ represent analysis tools, and $f$ and $g$ are the objective and constraint functions respectively. 
    Equation \ref{eqn:simple} makes an inherent assumption about the solution strategy for the problem. 
    Analysis $A$ outputs $z$, which is an input to $B$. Hence, $A$ should be run before $B$ with 
    with $y$ being iterated on to convergence with $y^t$. However, a slightly different formulation is 
    equally valid and still represents the exact same problem:

    \begin{align}
        given & \ \ B: {x,z} \rightarrow {y} \notag
        \\      & \ \ A: {x,y} \rightarrow {m,z^t} \notag
        \\min. &\ \ f(m) \notag
        \\w.r.t. & \ \ x,y,z \notag
        \\s.t. & \ \ g(z^t,z) = 0
        \label{eqn:simple2}
    \end{align}

    Equation \ref{eqn:simple2} differs only slightly from Eq. \ref{eqn:simple}. 
    $A$ is now dependent on the output of $B$, and $z$ will be iterated on to 
    convergence with $z^t$. Now the problem can be solved by running $B$ first 
    and then $A$.Since the formulations in Eqs. \ref{eqn:simple} and 
    \ref{eqn:simple2} both describe the same problem then neither can be the
    FPF. They are both specific versions of a more fundamental description of 
    the problem that is common between them. We present the fundamental 
    formulation as follows:

    \begin{align}
        given & \ \ A: {x,y} \rightarrow {m,z^t} \notag
        \\      & \ \ B: {x,z} \rightarrow {y^t} \notag
        \\min. &\ \ f(m) \notag
        \\w.r.t. & \ \ x,y,z \notag
        \\s.t. & \ \ g1(z^t,z) = 0 \notag
        \\     & \ \ g2(y^t,y) = 0
        \label{eqn:simple_fpf}
    \end{align}

    The formulation in Eq. \ref{eqn:simple_fpf} differs from both Eq. \ref{eqn:simple} 
    and Eq. \ref{eqn:simple2} because it has two constraints which both must be 
    met. The presence of both of these constraints fully decouples the problem so that 
    either $A$ or $B$ could be run first or both could be run simultaneously. 
    Alexandrov and Lewis, in their work with REMS, assert that fully decoupling 
    the analyses is key to achieving reconfigurability in the problem 
    formulation\cite{alexandrov2004}.

@@

    Steward's Design Structure Matrix (DSM) is a square adjacency matrix which captures the relationship between analysis tools where off 
    diagonal elements of the matrix indicate coupling\cite{Steward1981}. Since a DSM describes a square adjacency matrix, 
    it can be represented in an equivalent directed graph where nodes represent analysis tools and 
    edges represent information dependence between those tools. The ordering of elements in a DSM can be used to indicate 
    execution order.  For more complex problems, choosing the proper order to run analysis tools is a non-trival task. 
    Rogers et. al developed DeMAID to manipulate a DSM to find an ordering for analysis tools that 
    reduces the cost of solving highly coupled systems\cite{Rogers1996,rogers1996demaid}. This re-ordering is done through 
    row operations on the DSM matrix and yields multiple specific problem 
    formulations which all solve the same FPF. In other words, manipulation of the DSM does not fundamentally alter
    the problem formulation, which makes DSM an excellent foundation for specifying the FPF itself.

>>>>

    The Fundamental Problem Formulation (FPF) for any given problem will be constant regardless 
    of which MDAO framework, optimization algorithm, iterative solver, or solution strategy
    is used to solve the problem. However, it is possible to formulate a problem
    with an assumed execution ordering that implies a solution strategy. 
    For example, consider the Sellar test problem \cite{AIAA:sellar}:

    \begin{align}
        given & \ \ y_1 = D_1(x_1,y_2,z_1,z_2) \notag
        \\      & \ \ y_2^t = D_2(y_1,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,y_2,z_1,z_2 \notag
        \\s.t. & \ \ G(y_2,y_2^t) = 0
        \label{eqn:simple}
    \end{align}

    $D_1$ and $D_2$ represent analysis tools, and $F$ and $G$ are the objective 
    and constraint functions respectively. Equation \ref{eqn:simple} makes an 
    inherent assumption about the solution strategy for the problem. Analysis 
    $D_1$ outputs $y_1$, which is an input to $D_2$. Hence, $D_1$ should be run 
    before $D_2$ with with $y_2$ being iterated on to convergence with $y_2^t$. 
    However, a slightly different formulation is equally valid and still 
    represents the exact same problem:

    \begin{align}
        given & \ \ y_2 = D_2(y_1,z_1,z_2) \notag
        \\      & \ \ y_1^t = D_1(x_1,y_2,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,y_2,z_1,z_2 \notag
        \\s.t. & \ \ G(y_1,y_1^t) = 0
        \label{eqn:simple}
    \end{align}

    Equation \ref{eqn:simple2} differs only slightly from Eq. \ref{eqn:simple}. 
    $D_1$ is now dependent on the output of $D_2$, and $y_1$ will be iterated on to 
    convergence with $y_1^t$. Now the problem can be solved by running $D_2$ first 
    and then $D_1$. Since the formulations in Eqs. \ref{eqn:simple} and 
    \ref{eqn:simple2} both describe the same problem then neither can be the
    FPF. They are both specific versions of a more fundamental description of 
    the problem that is common between them. We present the fundamental 
    formulation as follows:

    \begin{align}
        given & \ \ D_1.y_1 = D_1(x_1,y_2,z_1,z_2) \notag
        \\      & \ \ D_2.y_2 = D_2(y_1,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,y_2,z_1,z_2 \notag
        \\s.t. & \ \ G_1(D_1.y_1,D_2.y_1) = 0 \notag
        \\     & \ \ G_2(D_1.y_2,D_2.y_2) = 0
        \label{eqn:simple_fpf}
    \end{align}

    The formulation in Eq. \ref{eqn:simple_fpf} differs from both Eq. \ref{eqn:simple} 
    and Eq. \ref{eqn:simple2} because it has two constraints which both must be 
    met. The presence of both of these constraints fully decouples the problem so that 
    either $D_1$ or $D_2$ could be run first or both could be run simultaneously. 
    Alexandrov and Lewis, in their work with REMS, assert that fully decoupling 
    the analyses is key to achieving reconfigurability in the problem 
    formulation\cite{alexandrov2004}. The key feature they identify to allow this decoupling 
    is the creation of separate variables for each analysis so that a variable 
    is identified by its analysis and it's name. For example, in Eqn. \ref{eqn:simple}
    there is only one $y_1$ variable vs Eqn. \ref{eqn:simple_fpf} where 
    there are two ($D_1.y_1$ vs $D_2.y_1$).

@@

    Steward's Design Structure Matrix (DSM) is a square adjacency matrix which captures the relationship between analysis tools where off 
    diagonal elements of the matrix indicate coupling\cite{Steward1981}. Since a DSM describes a square adjacency matrix, 
    it can be represented in an equivalent directed graph where nodes represent analysis tools and 
    edges represent information dependence between those tools. The ordering of elements in a DSM can be used to indicate 
    execution order.  For more complex problems, choosing the proper order to run analysis tools is a non-trival task. 
    Rogers et. al developed DeMAID to manipulate a DSM to find an ordering for analysis tools that 
    reduces the cost of solving highly coupled systems\cite{rogers1996,rogers1996demaid}. This re-ordering is done through 
    row operations on the DSM matrix and yields multiple specific problem 
    formulations which all solve the same FPF. In other words, manipulation of the DSM does not fundamentally alter
    the problem formulation, which makes DSM an excellent foundation for specifying the FPF itself.
